---
title: "Metaanalysis"
author: "Sevinj Guluyeva"
date: today
format:  
  html:
    theme: lumen
    toc: true
    toc_float: true
title-block-banner: true
execute:
  echo: fenced
editor_options:
  chunk_output_type: console
---

```{r}
#| label = "setup",
#| include = FALSE
library(meta)
library(metafor)
library(dplyr)
library(ggplot2)
#setwd("")
```

# ASSIGNMENT 

1) Import the data from the `data\metaanalysis_data.xlsx` file. The data come from the meta-analysis study: [Todd et al., 2017 - Sex differences in children's toy preferences: A systematic review, meta‐regression, and meta‐analysis](https://onlinelibrary.wiley.com/doi/full/10.1002/icd.2064)

The study looks at various studies of children choosing what kind of toys they play with (stereotypically 'boy-toys' or stereotypically 'girl-toys'). Mean times (in seconds) of playing are recorded, along with sample sizes and standard errors (for boys playing with each kind of toys and for girls playing with each kind of toys).

There's also information about the studies (e.g. year) and a bit about quality.

Here's authors' descriptions to the data:

> Neutral toys (1 = neutral toys included; 2 = neutral toys not included); Parent present (1 = absent; 2 = minimal interaction; 3 = moderate or full interaction); Setting = location of study (1 = home; 2 = laboratory; 3 = nursery); Country = gender inequality index, a measure of how gender egalitarian the country was at the time the study took place.

> Note. Quality is assessed using Newcastle–Ottawa Quality Assessment Scale criteria adapted for this study. A star indicates that the study fulfilled this criterion; an X indicates that the
study did not fulfil this criterion. 
Case definition adequate: clear justification for the gendered nature of a toy, for example, based on research. 
Representativeness of cases: recruitment of consecutive participants. 
Selection of controls: whether boys and girls were comparable in terms of social background.
Parental opinion: whether parents' views on gender were measured.
Comparability of both groups: the toys were comparable (in size, shape, etc.) and if the boys and girls were comparable in age. 
Ascertainment of behaviour: Play behaviour was clearly defined. 
Same ascertainment method for both groups: The measurement of the outcome (time spent playing with toy) was clearly defined. 
Nonresponse rate: whether either nonuptake or dropout rates reported.

2) Experiment using what you've learned:

a) combine the effects
b) create a funnel plot (what do you see?)
c) check if methods / quality affect the results
d) does author gender affect it?

# Loading dataset  

```{r , echo = FALSE}
data <- readxl::read_excel("/Users/sevinjguluyeva/Downloads/metaanalysis_data.xlsx")
head(data)
```

## Use same code from case 2 at class 

```{r , echo = FALSE}
m.raw <- metacont(n.e = N_boys,
                  mean.e = Mean_boys_play_male,
                  sd.e = SD_boys_play_male,
                  n.c = N_girls,
                  mean.c = Mean_girls_play_female,
                  sd.c = SD_girls_play_female,
                  data = data,
                  studlab = paste(Study),
                  fixed = TRUE,
                  random = TRUE,
)
m.raw
```

Then  use `meta`package  I put our results into the `forest()` function:

### First observation :
```{r , echo = FALSE}
m.raw %>% forest(sortvar = TE, fontsize = 4.5, squaresize = 0.5, col.square = 'green')
```


### Second observation :
```{r , echo = FALSE}
m.raw %>% metareg(`Parental opinion` + `Representativeness of cases`)
```


### Third observation :
```{r , echo = FALSE}
m.raw %>% metareg(`Female authors` + `Male authors`)
```

After examining all three observation points, the conclusion reached is that the observations from the first portion are generally centered and even those that appear to be off-center are actually extremely close to the center, meaning that all of them have very small standard errors (SE). Parental opinion has a significant impact, as we can see when we continue with the second point. Switching to the third observation, it is evident that gender has no bearing on the outcomes.


# Funnel plot 
```{r , echo = FALSE}
m.raw %>% funnel()
```



```{r, echo = FALSE}
contour_levels <- c(0.90, 0.95, 0.99)
contour_colors <- c("darkgreen", "green", "lightgreen")
funnel(m.raw, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)
```
